Accurate Measurement of Bicycle Parameters

### 2010-10-20 papers/BMD2010/PhysicalParametersPoster/poster.tex
poster final draft

% First column with content
\begin{column}{\onecolwid}
  \begin{block}{Introduction}
    \rmfamily{
    Accurate measurements of a bicycle's physical parameters are required for
    realistic dynamic simulations and analysis. For the most basic models the
    geometry, mass, mass location and mass distributions of each rigid body
    must be measured. In particular, we are concerned with the measurement of
    the minimal bicycle
    parameters required for the benchmark bicycle presented
    in~\cite{Meijaard2007}. A set of 25 parameters is used to populate the
    model.
    The experimental methods described herein are based primarily on
    the work done in \cite{Kooijman2006} and \cite{Roland1971} but have been
    refined for improved accuracy and methodology. We measured the
    characteristics of six different bicycles, two of which were set up in two
    different configurations. We provide a total of eight different parameter sets
    that can be used with, but not limited to, the benchmark bicycle model. The
    accuracy of all the measurements are presented along with a comparison of
    the linear characteristics of the eight bicycles.
    }
  \end{block}
  \vskip2ex

@@

% Second Column
\begin{column}{\twocolwid}
  %\setbeamercolor{block title}{fg=red,bg=white}%frame color
  %\setbeamercolor{block body}{fg=black,bg=white}%body color

  \begin{block}{Accuracy}
    \rmfamily{
    Following the vain of \cite{Roland1971} we used error propagation theory to
    calculate accuracy of the 25 benchmark bicycle parameters. We estimate
    the standard deviation of the raw measurements. If $x$ is a parameter and is a function of
    the raw measurements, $u,v,\ldots$, then $x$ is a random variable defined as
    $x=f(u,v,\ldots)$. The sample variance of $x$ is defined as
    \begin{equation}
        s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
                s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
                2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
                + \ldots
        \label{eqn:variance}
    \end{equation}
    where $s_u$ is the variance and $s_{uv}$ is the covariance. If $u$ and $v$ are uncorrelated then $s_{uv}=0$ but the cross correlations
    must be taken into account otherwise.
    }
  \end{block}
  \begin{columns}[t, totalwidth=\twocolwid]
      \begin{column}{\onecolwid}
          \begin{block}{Bicycles}
            \rmfamily{
            The six bicycles, chosen for both variety and convenience, are as follows:
            \emph{Batavus Browser}, a Dutch style city bicycle measured with and without
            instrumentation; \emph{Batavus Stratos
            Deluxe}, a Dutch style sporty city bicycle; \emph{Batavus Crescendo Deluxe} a
            Dutch style city bicycle with a suspended fork; \emph{Gary Fisher Mountain
            Bike}, a hardtail mountain bicycle; \emph{Bianchi Pista}, a modern steel frame
            track racing bicycle; and \emph{Yellow Bicycle}, a stripped down aluminum frame
            road bicycle measured in two configurations, the second with the fork rotated
            in the headtube 180 degrees for larger trail.
            \\
            \begin{center}
                \begin{tabular}{ccc}
                    \includegraphics[width=0.333\onecolwid]{../../../images/browserIns_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/crescendo_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/fisher_sub.jpg}
                    \\
                    \includegraphics[width=0.333\onecolwid]{../../../images/pista_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/stratos_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/yellow_sub.jpg}
                \end{tabular}
            \end{center}
            }
          \end{block}
    \end{column}

@@

\begin{column}{\onecolwid}
  % Frequency Response
  \begin{alertblock}{Frequency Response}
    \small{\rmfamily{
    The steer torque to roll angle Bode plot reveals up to 10 dB variation
    among the bikes and variation in phase.
    }}
    \\
    \begin{center}
      \includegraphics[width=.85\onecolwid]{../../../plots/Bike/Bode/Tdel2phi.pdf}
      \\
      \includegraphics[width=.85\onecolwid]{../../../plots/BikeRider/Bode/Tdel2phi.pdf}
    \end{center}
  \end{alertblock}

>>>>

% First column with content
\begin{column}{\onecolwid}
  \begin{block}{Introduction}
    \rmfamily{
    Accurate estimates of a bicycle's physical parameters are required for
    realistic dynamic simulations and analysis. For the most basic models the
    geometry, mass, mass location and mass distribution of each rigid body
    must be measured. In particular, we are concerned with the measurement of
    the non-minimal set of 25 parameters required for the benchmark bicycle
    presented in~\cite{Meijaard2007}.
    The experimental methods described herein are based primarily on
    the work done in \cite{Kooijman2006} and \cite{Roland1971} but have been
    refined for improved accuracy and methodology. We measured the
    characteristics of six different bicycles, two of which were set up in two
    different configurations. We provide a total of eight different parameter sets
    that can be used with, but not limited to, the benchmark bicycle model. The
    accuracy of all the measurements are presented along with a comparison of
    the linear characteristics of the eight bicycles.
    }
  \end{block}
  \vskip2ex

@@

% Second Column
\begin{column}{\twocolwid}
  \begin{block}{Accuracy}
    \rmfamily{
    Following in the vain of \cite{Roland1971} we used error propagation theory to
    calculate the accuracy of the estimates of 25 benchmark bicycle parameters.
    We first estimate
    the standard deviation of the raw measurements. If $x$ is a parameter and is a function of
    the raw measurements, $u,v,\ldots$, then $x$ is a random variable defined as
    $x=f(u,v,\ldots)$. The sample variance of $x$ is defined as
    \begin{equation}
        s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
                s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
                2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
                + \ldots
        \label{eqn:variance}
    \end{equation}
    where $s_u$ is the variance and $s_{uv}$ is the covariance. If $u$ and $v$ are uncorrelated then $s_{uv}=0$ but the cross correlations
    must be taken into account otherwise.
    }
  \end{block}
  \begin{columns}[t, totalwidth=\twocolwid]
      \begin{column}{\onecolwid}
          \begin{block}{Bicycles}
            \rmfamily{
            The six bicycles, chosen for both variety and convenience, are as follows:
            \emph{Batavus Browser}, a Dutch style city bicycle measured with and without
            instrumentation; \emph{Batavus Stratos
            Deluxe}, a Dutch style sporty city bicycle; \emph{Batavus Crescendo Deluxe} a
            Dutch style city bicycle with a suspended fork; \emph{Gary Fisher Mountain
            Bike}, a hardtail mountain bicycle; \emph{Bianchi Pista}, a modern steel frame
            track racing bicycle; and \emph{Yellow Bicycle}, a stripped down aluminum frame
            road bicycle measured in two configurations, the second with the fork rotated
            in the headtube 180 degrees for larger trail.
            \\
            \begin{center}
                \begin{tabular}{ccc}
                    \includegraphics[width=0.333\onecolwid]{../../../images/browserIns_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/crescendo_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/fisher_sub.jpg}
                    \\
                    \includegraphics[width=0.333\onecolwid]{../../../images/pista_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/stratos_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/yellow_sub.jpg}
                \end{tabular}
            \end{center}
            }
          \end{block}
    \end{column}

@@

\begin{column}{\onecolwid}
  % Frequency Response
  \begin{alertblock}{Frequency Response}
    \small{\rmfamily{
    The steer torque to roll angle Bode plot reveals up to 10 dB variation
    among the bikes and variation in phase below 10 rad/s.
    }}
    \\
    \begin{center}
      \includegraphics[width=.85\onecolwid]{../../../plots/Bike/Bode/Tdel2phi.pdf}
      \\
      \includegraphics[width=.85\onecolwid]{../../../plots/BikeRider/Bode/Tdel2phi.pdf}
    \end{center}
  \end{alertblock}
